### 2014-06-29 2/literature_review.tex
auto

There have been several other attempts to filter POLSAR data.
Vasile, proposed a region growing adaptive neighbourhood approach in 2006, where averaging is performed on an adaptive homogenous neighbour.
The main drawback of the approach is that only the intensity was used to determine homogeneity and a primitive averaging filter is performed on off-diagonal elements \cite{Vasile_TGRS_2006}.
%J.S. Lee is also very active in POLSAR speckle filtering.
In \cite{Lee_2006_TGRS}, J.S. Lee proposed to group homogenous pixels based on their underlying scattering model. 
While the work is interesting, it is believed that pixels having similar underlying models, for example volume scattering, can still be of a very different nature.
Similar to Lee's previous work, a simple weighted average filtering is applied on both diagonal and off-diagonal elements.
Vasile, in 2010, published a complicated spherically invariant random vector estimation scheme to estimate the underlying target POLSAR signature \cite{Vasile_2010_TGRS}.
While polarimetric information is estimated independently from the power span, its output results no longer follow established Wishart distribution.

>>>>

There have been several other attempts to filter POLSAR data.
Vasile, proposed a region growing adaptive neighbourhood approach in 2006, where averaging is performed on an adaptive homogeneous neighbour.
The main drawback of the approach is that only the intensity was used to determine homogeneity and a primitive averaging filter is performed on off-diagonal elements \cite{Vasile_TGRS_2006}.
%J.S. Lee is also very active in POLSAR speckle filtering.
In \cite{Lee_2006_TGRS}, J.S. Lee proposed to group homogeneous pixels based on their underlying scattering model. 
While the work is interesting, it is believed that pixels having similar underlying models, for example volume scattering, can still be of a very different nature.
Similar to Lee's previous work, a simple weighted average filtering is applied on both diagonal and off-diagonal elements.
Vasile, in 2010, published a complicated spherically invariant random vector estimation scheme to estimate the underlying target POLSAR signature \cite{Vasile_2010_TGRS}.
While polarimetric information is estimated independently from the power span, its output results no longer follow established Wishart distribution.

### 2014-06-29 3/sar.tex
auto

%The nature of SAR speckle is stochastic over homogeneous areas and heteroskedastic heterogeneously.
As shown in the previous section,
  over heterogeneous area, the stochastic SAR speckle is heteroskedastic in nature.
Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
While the statistical model within individual resolution cells is well established,
  it is only applicable to homogeneous areas.
Practical images, however, are heterogeneous.
Furthermore, it is precisely this spatial variation that is often of high interest.
%And while the statistical model within individual resolution cells is well established,
%  the applicability of these models, however, are restricted to homogeneous areas. 
%Practical images, nevertheless, are heterogeneous. 
%Crucially it is this spatial variation that is of high interest. 
%This fact gives rise to the question that seemed obvious:
  %how to call an analysis area heterogeneous and subsequently
%  what to do in the case of heterogeneity.

@@

To experimentally validate this theoretical discussion, real world data is extracted from a known  homogenous area (from within a RADARSAT2 image). The PDF histogram from this data is then plotted in 
Fig. \ref{fig:modelled_response} along with the modelled PDF response. 
The excellent agreement observable between the real world and modelled data tends to validate the log-transformed model. 
%In fact, this modelling has been used successful in explaining speckle phenomena, also verified 
%through scientific experiments \cite{Ulaby_TGRS_1988}.

\begin{figure}[!h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/intensity_histogram.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_intensity_histogram.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram of a homogenous area and modelled PDF response}
\label{fig:modelled_response}
\end{figure}

>>>>

%The nature of SAR speckle is stochastic over homogeneous areas and heteroskedastic heterogeneously.
As shown in the previous section,
  the stochastic SAR speckle, over heterogeneous area, exhibits heteroskedastic properties.
Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
While the statistical model within individual resolution cells is well established,
  it is only applicable to homogeneous areas.
Practical images, however, are heterogeneous.
Furthermore, it is precisely this spatial variation that is often of high interest.
%And while the statistical model within individual resolution cells is well established,
%  the applicability of these models, however, are restricted to homogeneous areas. 
%Practical images, nevertheless, are heterogeneous. 
%Crucially it is this spatial variation that is of high interest. 
%This fact gives rise to the question that seemed obvious:
  %how to call an analysis area heterogeneous and subsequently
%  what to do in the case of heterogeneity.

@@

To experimentally validate this theoretical discussion, real world data is extracted from a known  homogeneous area (from within a RADARSAT2 image). The PDF histogram from this data is then plotted in 
Fig. \ref{fig:modelled_response} along with the modelled PDF response. 
The excellent agreement observable between the real world and modelled data tends to validate the log-transformed model. 
%In fact, this modelling has been used successful in explaining speckle phenomena, also verified 
%through scientific experiments \cite{Ulaby_TGRS_1988}.

\begin{figure}[!h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/intensity_histogram.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_intensity_histogram.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram of a homogeneous area and modelled PDF response}
\label{fig:modelled_response}
\end{figure}

### 2014-06-29 5/applications.tex
auto

{\small
\lstset{language=Matlab,caption=Homogeneous partitions number growing,label=lst:k_mle_algo_partition_number}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
\begin{lstlisting}[frame=tb]
function centers = partition_into_homogenous_groups(l, threshold)
  c_init = maximum_likelihood_of(l);
  [further_partition_needed, c_new] = 
          check_homogeneity_status(l, c_init, threshold);

  while (further_partition_needed) do
    c_prev = c_new;
    c_new = k_mle_cluster(l, c_prev);
    [further_partition_needed, c_new] = 
            check_homogeneity_status(l, c_prev, threshold);    
  end while
  %after this: all paritions are homogenous

@@

  m[i,j] = get_membership_assigments(l, c);
  all_partitions_homogenous = true;
  c_new = c;
  for (j = 1 to size_of(c)) 
    g = {L[i] with m[i,j]==1};
    this_partition_homogenous = 
      (variance(g) < threshold_vector[size_of(g)]);

    if (NOT this_partition_homogenous) then
      % split non-homogenous partition
      c_new[j] = min(g);
      c_new[size_of(c_new) + 1] = max(g);

      all_partitions_homogenous = false;
    end if
  end for

  further_partition_needed = NOT all_partitions_homogenous;
end function
\end{lstlisting}

@@

We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Looks value.
Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002_721}, the formula is given as:
$MSE = \frac{1}{(ENL - 0.5)ln^2(2)}$.
%An experiment is carried out to 
Fig. \ref{fig:verify_MSE_as_perf_index} demonstrates the relationship.
The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
This is illustrated with ``tighter'' distance histograms and reducing Mean Squared Error (MSE), as plotted in Fig. \ref{fig:Homogeneous_Area}

@@

\begin{figure}
\centering
      \begin{tabular}[h]{c}
 	\subfloat[SLC Intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/illustrate_ROC_curve.pdf.s.made.eps} 
		 \label{fig:illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[9-Look Intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/illustrate_ROC_curve.pdf.m.made.eps} 
		 \label{fig:illustrate_ROC_curve.pdf.m.made.eps}
	} \\
 	\subfloat[SLC log-intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/log_illustrate_ROC_curve.pdf.s.made.eps} 
		 \label{fig:log_illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[9-Look log-intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/log_illustrate_ROC_curve.pdf.m.made.eps} 
		 \label{fig:log_illustrate_ROC_curve.pdf.m.made.eps}
	}
   \end{tabular}
\caption{Histogram discriminality and the ROC Curve}
\label{fig:PDF_Discriminality}
\end{figure}

@@

The most common types of target to be detected in image processing are point targets, line targets, and edge targets.
The detectability of these targets are measured using the AUC index which is tabulated against the MSE.
Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of f-MLE filters for artificially-generated heterogenous test regions.
Apparently the f-MLE filters have better performance than boxcar filters.
Also noticeable is the correlation between MSE and the Area Under the ROC curve criteria, 
  which is an interesting phenomena that will be investigated further in the next section.
%Even though the relationship is probably not linear,
%  the correlation between MSE and Area Under the ROC curve (AUC) is apparent,

>>>>

{\small
\lstset{language=Matlab,caption=Homogeneous partitions number growing,label=lst:k_mle_algo_partition_number}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
\begin{lstlisting}[frame=tb]
function centers = partition_into_homogeneous_groups(l, threshold)
  c_init = maximum_likelihood_of(l);
  [further_partition_needed, c_new] = 
          check_homogeneity_status(l, c_init, threshold);

  while (further_partition_needed) do
    c_prev = c_new;
    c_new = k_mle_cluster(l, c_prev);
    [further_partition_needed, c_new] = 
            check_homogeneity_status(l, c_prev, threshold);    
  end while
  %after this: all paritions are homogeneous

@@

  m[i,j] = get_membership_assigments(l, c);
  all_partitions_homogeneous = true;
  c_new = c;
  for (j = 1 to size_of(c)) 
    g = {L[i] with m[i,j]==1};
    this_partition_homogeneous = 
      (variance(g) < threshold_vector[size_of(g)]);

    if (NOT this_partition_homogeneous) then
      % split non-homogeneous partition
      c_new[j] = min(g);
      c_new[size_of(c_new) + 1] = max(g);

      all_partitions_homogeneous = false;
    end if
  end for

  further_partition_needed = NOT all_partitions_homogeneous;
end function
\end{lstlisting}

@@

We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Looks value.
Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002_721}, the formula is given as:
$MSE = \frac{1}{(ENL - 0.5)ln^2(2)}$.
%An experiment is carried out to 
Fig. \ref{fig:verify_MSE_as_perf_index} demonstrates the relationship.
The ``simulated result'' plot is computed through a Monte Carlo simulation.
And the ``analysis formula'' is a straight forward plotting of the mathematical formula above.
The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
This is illustrated with ``tighter'' distance histograms and reducing Mean Squared Error (MSE), as plotted in Fig. \ref{fig:Homogeneous_Area}

@@

\begin{figure}[h]
\centering
      \begin{tabular}{c}
 	\subfloat[][SLC Intensity]{
%		 \epsfxsize=6cm
%		 \epsfysize=6cm
%		 \epsffile{images/illustrate_ROC_curve.pdf.s.made.eps} 
                 \plotWithLegend{images/illustrate_ROC_curve.pdf.s.made.eps}{SLC log-intensity} 
		 \label{fig:illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[][9-Look Intensity]{
%		 \epsfxsize=6cm
%		 \epsfysize=6cm
%		 \epsffile{images/illustrate_ROC_curve.pdf.m.made.eps} 
                 \plotWithLegend{images/illustrate_ROC_curve.pdf.m.made.eps}{SLC log-intensity} 
		 \label{fig:illustrate_ROC_curve.pdf.m.made.eps}
	} \\
 	\subfloat[][SLC log-intensity]{
%		 \epsfxsize=6cm
%		 \epsfysize=6cm
%		 \epsffile{images/log_illustrate_ROC_curve.pdf.s.made.eps} 
                 \plotWithLegend{images/log_illustrate_ROC_curve.pdf.s.made.eps}{SLC log-intensity} 
		 \label{fig:log_illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[][9-Look log-intensity]{
%		 \epsfxsize=6cm
%		 \epsfysize=6cm
%		 \epsffile{images/log_illustrate_ROC_curve.pdf.m.made.eps} 
                 \plotWithLegend{images/log_illustrate_ROC_curve.pdf.m.made.eps}{9-Look log-intensity} 
		 \label{fig:log_illustrate_ROC_curve.pdf.m.made.eps}
	}
   \end{tabular}
\caption{Histogram discriminality and the ROC Curve}
\label{fig:PDF_Discriminality}
\end{figure}

@@

The most common types of target to be detected in image processing are point targets, line targets, and edge targets.
The detectability of these targets are measured using the AUC index which is tabulated against the MSE.
Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of f-MLE filters for artificially-generated heterogeneous test regions.
Apparently the f-MLE filters have better performance than boxcar filters.
Also noticeable is the correlation between MSE and the Area Under the ROC curve criteria, 
  which is an interesting phenomena that will be investigated further in the next section.
%Even though the relationship is probably not linear,
%  the correlation between MSE and Area Under the ROC curve (AUC) is apparent,
